The K2 Halo Photometry Campaign

### 2019-04-03 paper/ms.tex
figures
meta optimizing

\section{Halo Photometry}
\label{sec:k2}

@@

\noindent which is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$. For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation as used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. The lag parameter $l$ allow for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below. The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise. TV is a convex objective function \textcolor{red}{and I think the generalizations are too} and $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.

@@

@@

% benchmarking with lags and

@@

\begin{figure*}
\plottwo{lag_lc_cdpp.pdf}{lag_sc.pdf}
\caption{Behaviour of long cadence (left) and short cadence (right) CDPP as a function of lag parameter $l$. For long cadence this shows a minimum for L1 norm and $l=10$, i.e. for objective function $\Lambda_{1,10}$. For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1, L2 or~L3 norms.}
\end{figure*}

@@

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were not only assigned long-cadence halo apertures, but also downloaded at short cadence. For these targets we have provided both long and short cadence reductions. Following the analysis in Section~\ref{optimization} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$~cad and on choice of objective function, for consistency with  long cadence we have adopted a 300~cadence lag (i.e. $30 \times$ the long cadence lag of 10) and the L1 TV objective function. With their long timeseries the short cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo lightcurves.

>>>>

\section{Halo Photometry Method}
\label{method}

@@

\noindent which is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$. For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation as used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. The lag parameter $l$ allow for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below. The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise. TV is a convex objective function \textcolor{red}{and I think the generalizations are too} and $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.

@@

% benchmarking with lags and objective functions

In order to choose the objective function $\Lambda_{k,l}$, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the halo sample and one with very little high frequency variability detected or predicted, which was also observed at short cadence. We choose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better. We calculate halo lightcurves and their CDPPs for $k \in \{1,2,3\}$, and $l \in [1,50]$ for long cadence and (sparsely) $l \in [1,2500]$ for short cadence data. The results are displayed in Figure~\ref{cdpps}. We find that for long cadence data, the L1 norm (TV) and a lag of 10 provide the best CDPP, which is unsurprising given that this is a slightly shorter lag than the 12~cadence thruster firing period. In this context we can understand the optimum as TV-min suppressing systematics on the same timescale as they occur. On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for all values of $k$ and improves very slowly with $l$ for longer lags. In calculating lightcurves here, seeing the very weak dependence of short cadence CDPP on $l$, we calculate our final light curves with TV and a lag of 300 cadences for consistency with the long cadence method.

\begin{figure*}
\plottwo{lag_lc_cdpp.pdf}{lag_sc.pdf}
\caption{Behaviour of long cadence (left) and short cadence (right) 6.5~hour CDPP for the quiet dwarf 36~Ophiuchi as a function of lag parameter $l$. For long cadence this shows a minimum for L1 norm and $l=10$, i.e. for objective function $\Lambda_{1,10}$. For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1, L2 or~L3 norms.}
\label{cdpps}
\end{figure*}

@@

In addition to these changes in objective function, we have also added a feature `\texttt{deathstar}' to deal with contamination. We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out. \textcolor{red}{More here from Tim.}

@@

@@

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were not only assigned long-cadence halo apertures, but also downloaded at short cadence. For these targets we have provided both long and short cadence reductions. Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$~cad and on choice of objective function, for consistency with  long cadence we have adopted a 300~cadence lag (i.e. $30 \times$ the long cadence lag of 10) and the L1 TV objective function. With their long timeseries the short cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo lightcurves.
